The Emergent Simplicity of Galaxy Size

### 2017-09-15 paper/galsize_paper.tex
Updated simulation information

\subsection{Galaxy Sample and Measurements}
\label{subsec:galaxydata}

@@

@@

\subsection{Simulation and Halos}
\label{subsec:sim}

{\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation are the basis of all our modeling.

\subsection{Baseline Model and Mock Measurements}
\label{subsec:baselinemock}

\subsubsection{Mapping $\mstar$ \& $\sfr$ to halos}
\label{subsubsec:umachine}

The starting point of our model is the best-fit {\tt UniverseMachine} model \citep[][in prep]{behroozi_etal17}. This model maps stellar mass and star-formation rate to every halo and subhalo at each snapshot in the Bolshoi-Planck simulation. The stellar mass function, quenched fraction, SFR density, and SFR-dependent clustering are all accurately captured by this model from $z=0-10.$ The model we have developed in the present work does not depend in an essential way upon the {\tt UniverseMachine} model in particular; we only require some reasonably accurate starting point for the $\mstar$ and $\ssfr$ values mapped to simulated halos.

\subsubsection{Mapping $\bt$ to halos}
\label{subsubsec:random_bt_model}

Our model for galaxy size is further predicated upon the mapping between dark matter halos and $\bt,$ the fraction of stellar mass in the bulge. In a companion paper to this work, we will present a separate empirical model for the $\bt-$halo connection. For our present purposes, we instead rely upon the simplest possible assumption for this connection that recovers the observed distribution $P(\bt\vert\mstar,\ssfr):$ we suppose that galaxy $\bt$ has no dependence whatsoever upon halo environment or assembly, beyond what is inherited by the mutual correlation between $\mstar, \ssfr$ and the cosmic web. That is, we map $\bt$ to dark matter halos by using the $\mstar$ and $\ssfr$ values from {\tt UniverseMachine} to randomly select the $\bt$ of a galaxy from our SDSS sample with a similar $\mstar$ and $\ssfr.$ The intuitive interpretation of this modeling choice is that we assume the morphology-density relation is entirely determined by the color-density relation.

\subsection{Mock Measurements of Clustering and Lensing}
\label{subsec:mock_measurements}

For mock galaxies, to compute galaxy clustering we employ the distant observer approximation by treating the simulation $z-$axis as the line-of-sight. We compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}. We compute lensing $\Delta\Sigma$ using the {\tt mock\_observables.delta\_sigma} function in {\tt Halotools} to calculate the two-dimensional surface mass density of a random downsampling of $10^6$ dark matter particles in the snapshot.

\section{Galaxy Profile Model}
\label{sec:model}

@@

>>>>

@@

As the bedrock of our modeling, we use the catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,behroozi12_rockstar,behroozi12_consistent_trees,riebe_etal13,rodriguez_puebla16_bolplanck}. the particular version of the catalog we use is made publicly available through {\tt Halotools} \citep{hearin_etal16}, with {\tt version\_name} = `halotools\_v0p4'. For mock galaxies, to compute galaxy clustering we employ the distant observer approximation by treating the simulation $z-$axis as the line-of-sight. We compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.

@@

\section{Galaxy-Halo Model}
\label{sec:model}

@@

APH thanks John Baker for the {\em Toejam \& Earl} soundtrack.
